\documentclass[11pt]{article}

% ==== PACKAGES ==== %
% \usepackage{fullpage}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{epic}
\usepackage{eepic}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{bbm}
\usepackage[letterpaper, margin=1in]{geometry}

% ==== MARGINS ==== %
% \pagestyle{empty}
% \setlength{\oddsidemargin}{0in}
% \setlength{\textwidth}{6.8in}
% \setlength{\textheight}{9.5in}

\pagestyle{fancy}
\fancyhf{}
\rhead{CSCI 5229}
\lhead{Homework 1}
\rfoot{Page \thepage}


\newtheorem*{solution*}{Solution}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{definition}[lemma]{Definition}
\newtheorem{corollary}[lemma]{Corollary}
\lstset{moredelim=[is][\bfseries]{[*}{*]}}

% ==== DOCUMENT PROPER ==== %
\begin{document}

\thispagestyle{empty}

% --- Header Box --- %
\newlength{\boxlength}\setlength{\boxlength}{\textwidth}
\addtolength{\boxlength}{-4mm}

\begin{center}\framebox{\parbox{\boxlength}{\bf
      Computer Graphics \hfill Homework 1\\
      CSCI 5229 Fall 2018 \hfill Due Date: Sep 5, 2018\\
      Name: Andrew Kramer \hfill CU identitykey: ankr1041
}}
\end{center}




\section{Gears Program}

\subsection{List the framerate reported by the program when the window is at different sizes}

\subparagraph{}

When run on my macbook pro \textit{gears} runs at $60$ frames per second regardless of the window size. When run on my desktop, which runs ubuntu, \textit{gears} runs at $7300$ fps when the window size is $1280\times1024$, $16800$ when the window size is $300\times300$, and $17000$ fps when the window size is $1\times1$.

\subsection{On some systems the frame rate is a small round number like $60$ or $72$ or $85$ frames per second, and sometimes it is a large number, thousands or tens of thousands of frames per second. Explain why this occurs.}

\subparagraph{}

When vsync is enabled the framerate will be synchronized to the refresh rate of the monitor. This is why the framerate was limited to $60$ frames per second on my macbook pro. Initially, my ubuntu machine showed the same behavior, but when I disabled vsync I saw the much higher framerates reported in the answer to question 1. I was unable to disable vsync on my macbook. This is why I was only able to perform this experiment on my ubuntu machine.

\subsection{Time required to complete the assignment}

\subparagraph{}

Approximately one hour.


\end{document}
